Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-03 submission/paper-submission.Rnw
adding the paper files and code for submission

# Specify global options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.keep = 'high',
  fig.align = 'center',
  dev = c("cairo_pdf", "cairo_ps"),
  dev.args = list(fallback_resolution = 800),
  dpi = 1200
)

@@

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("../data/sine_lime_explain.rds")) {

@@

    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")

@@

    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")

@@

# Load the hamby data
bullet_train <- read.csv("../data/hamby173and252_train.csv")
bullet_test <- read.csv("../data/hamby224_test.csv")

@@

# Convert the bullet figure to eps (if needed)
if (!file.exists("./figure-static/figure-08-1.eps")) {
  bullets <- image_read("./figure-static/figure-08-1.png")
  image_write(bullets, path = "./figure-static/figure-08-1.eps", format = "eps")
}

# Load and print the plot
knitr::include_graphics("./figure-static/figure-08-1.eps")

@@

# Load the signatures data
signatures <- readRDS("../data/signatures.rds")

@@

# Create (or load) the parallel coordinate plot
if (!file.exists("./figure-static/figure-10-1.png")) {

@@

  # Save the plot
  ggplot2::ggsave(
    plot = bullet_pcp,
    filename = "./figure-static/figure-10.png",
    width = 7.5,
    height = 3.5,
    units = "in",
    dpi = 1200
  )

@@

# Create (or load) the parallel coordinate plot
if (file.exists("./figure-static/figure-10-1.eps")) {

  # Load and print the plot
  knitr::include_graphics("./figure-static/figure-10-1.eps")

  # Load the figure and then save as an eps file
  bullet_pcp <- image_read("./figure-static/figure-10-1.png")
  image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")

@@

# Apply LIME to all but two cases without returning the permutations
if (file.exists("../data/hamby_lime.rds")){

  # Load the files
  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")

@@

  # Save the output objects
  saveRDS(object = bullet_lime_noperms,
          file = "../data/hamby_lime.rds")
  saveRDS(object = bullet_explain_noperms,
          file = "../data/hamby_explain.rds")

>>>>

# Specify global options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.keep = 'high',
  fig.align = 'center',
  dev = c("cairo_pdf", "cairo_ps"),
  dev.args = list(fallback_resolution = 800),
  dpi = 1200,
  fig.path = ""
)

@@

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("sine_lime_explain.rds")) {

@@

    saveRDS(sine_lime_explain, "sine_lime_explain.rds")

@@

    sine_lime_explain <- readRDS("sine_lime_explain.rds")

@@

# Load the hamby data
bullet_train <- read.csv("hamby173and252_train.csv")
bullet_test <- read.csv("hamby224_test.csv")

@@

# Convert the bullet figure to eps (if needed)
if (!file.exists("figure-08-1.eps")) {
  bullets <- image_read("figure-08-1.png")
  image_write(bullets, path = "figure-08-1.eps", format = "eps")
}

# Load and print the plot
knitr::include_graphics("figure-08-1.eps")

@@

# Load the signatures data
signatures <- readRDS("signatures.rds")

@@

# Create (or load) the parallel coordinate plot
if (!file.exists("figure-10-1.png")) {

@@

  # Save the plot
  ggplot2::ggsave(
    plot = bullet_pcp,
    filename = "figure-10.png",
    width = 7.5,
    height = 3.5,
    units = "in",
    dpi = 1200
  )

@@

# Create (or load) the parallel coordinate plot
if (file.exists("figure-10-1.eps")) {

  # Load and print the plot
  knitr::include_graphics("figure-10-1.eps")

} else {on

  # Load the figure and then save as an eps file
  bullet_pcp <- image_read("figure-10-1.png")
  image_write(bullet_pcp, path = "figure-10-1.eps", format = "eps")

@@

# Apply LIME to all but two cases without returning the permutations
if (file.exists("hamby_lime.rds")){

  # Load the files
  bullet_explain_noperms <- readRDS("hamby_explain.rds")

@@

  # Save the output objects
  saveRDS(object = bullet_lime_noperms,
          file = "hamby_lime.rds")
  saveRDS(object = bullet_explain_noperms,
          file = "hamby_explain.rds")
